Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
edit design principles + related

In the previous iteration of Wildcard, web scraping was an entirely
separate activity from customization. Programmers that wrote scraping
adapters would need to switch into an IDE to write code as part of
customizing a new website.

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{import.io},
dexi.io \citep{dexi.io}, Octoparse \citep{octoparse} and ParseHub
\citep{parsehub}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow.

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This directly
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} being
an integral part of end-user programming systems.

@@

In Wildcard, if a website's hand-coded adapter ceases to function
because the website changes, the table may lose its data which means
that an end-user's customizations may also cease to function.
Furthermore, end-users are powerless to extend the scraping adapter to
add columns to the table in order to perform new customizations. This
goes against MacLean et. al.'s vision of user-tailorable systems
\citep{maclean1990} that give users ``a feeling of ownership of the
system, to feel in control of changing the system and to understand what
can be changed.'' Providing an easy way for users to edit programs is
therefore fundamental to fully democratizing web customization.

@@

In many programming-by-demonstration web scraping systems
\citep[\citet{lin2009}]{chasins2018}, users only get \emph{full}
feedback about the program's execution (generalization and the scraped
values) after providing \emph{all} the demonstrations. This means they
cannot adjust their demonstrations in response to the system's feedback
as they demonstrate.

>>>>

In the previous iteration of Wildcard, web scraping was an entirely
separate activity from customization. Programmers that wrote scraping
adapters would need to switch into an IDE to write code as part of
customizing a new website. This divide between tasks is common in other
domains:

\begin{itemize}
\tightlist
\item
  In \textbf{data science}, workflows revolve between cleaning and using
  data but this often happens in different environments. The creators of
  Wrex \citep{drosos2020}, an end-user programming-by-example system for
  data wrangling, reported that ``although data scientists were aware of
  and appreciated the productivity benefits of existing data wrangling
  tools, having to leave their native notebook environment to perform
  wrangling limited the usefulness of these tools.'' This was a major
  reason Wrex was developed as an add-on to Jupyter notebooks, the
  environment in which data scientists use their data.
\item
  In \textbf{web scraping,} if a user comes across an omission while
  working with data scraped from a website, they need to switch from the
  environment in which they are using the data to the environment in
  which they created their scraping code in order to edit and re-run it.
  This can be seen in many end-user web scraping systems like Rousillon
  \citep{chasins2018}and FlashExtract \citep{le2014} and commercial
  tools like import.io \citep{import.io}, dexi.io \citep{dexi.io},
  Octoparse \citep{octoparse} and ParseHub \citep{parsehub}.
\item
  In \textbf{web customization}, the creators of Vegemite
  \citep{lin2009}, a system for end-user programming of mashups,
  reported that participants of its user study thought ``it was
  confusing to use one technique to create the initial table, and
  another technique to add information to a new column.'' This hints at
  the need for both a unified environment and a unified workflow.
\end{itemize}

In this work, we have combined scraping and customization into a single,
unified environment with a unified workflow. The goal is to minimize the
environment switch between \emph{extracting} the data and \emph{using}
the data. A user might start out by scraping some data on a website, and
then switch to customizing the website using the results. Then, they
might realize they need more data to perform their desired task, at
which point they can easily extend the adapter by demonstrating new
columns. All of these tasks take place right in the browser, where the
user was initially already using the website. Instead of bringing the
data to another tool, we have brought a tool to the data. This principle
relates to the idea of ``in-place toolchains'' \citep{zotero-1362} for
end-user programming systems: that users should be able to program using
familiar tools in the context where they already use their software.

@@

In the prior iteration of Wildcard, if a website's hand-coded adapter
stops working correctly because the website changes, an end-user's
customizations will often break too. Furthermore, end-users cannot
extend the scraping adapter to add columns to the table in order to
perform new customizations. This goes against MacLean et. al.'s vision
of user-tailorable systems \citep{maclean1990} that give users ``a
feeling of ownership of the system, to feel in control of changing the
system and to understand what can be changed.'' Providing an easy way
for users to edit programs is therefore fundamental to fully
democratizing web customization.

@@

In many programming-by-demonstration web scraping systems
\citep{chasins2018, lin2009}, users only get \emph{full} feedback about
the program's execution (generalization and the scraped values) after
providing \emph{all} the demonstrations. This means they cannot adjust
their demonstrations in response to the system's feedback as they
demonstrate.
